---
title: "Summarize CO survey flagging of suspicious responses"
date: '`r strftime(Sys.time(), format = "%B %d, %Y")`'
output: github_document
---

```{r setup, message=FALSE}
library(tidyverse)
knitr::opts_chunk$set(comment = NA)
```

```{r}
svy_all <- readRDS("../../data-work/1-svy/svy-reshape.rds")
svy <- readRDS("../../data-work/1-svy/svy-clean.rds")
flags <- readRDS("../../data-work/1-svy/svy-flag.rds")

# a few "none" activity people are dropped from the flag table
# (they were filtered out in the 4-clean step since they shouldn't have gotten the survey)
flags$flag_values <- flags$flag_values %>%
    semi_join(svy$person, by = "Vrid")
```

## Overview

A set of tests were run to flag respondents for possible removal from survey analysis, based on suspicious responses. Each instance of a suspicious response is assigned a defined flag value, and flags sum (i.e., a respondent can accumulate multiple flags). 

### Flags used

```{r}
# counts by flag
cnt <- flags$flag_values %>% count(flag_name)
left_join(flags$flag_details, cnt, by = "flag_name") %>%
    knitr::kable()
```

### Core Flags

Core flags are those marked core_suspicious in the first table.

```{r}
flags$flag_values %>%
    filter(group == "core_suspicious") %>%
    group_by(Vrid) %>%
    summarise(flags = sum(value)) %>%
    count(flags) %>%
    arrange(desc(flags)) %>%
    mutate(cumulative_n = cumsum(n)) %>%
    knitr::kable()
```

### Missing Responses

```{r}
flags$flag_values %>%
    filter(group == "incomplete") %>%
    group_by(Vrid) %>%
    summarise(flags = sum(value)) %>%
    count(flags) %>%
    arrange(desc(flags)) %>%
    mutate(cumulative_n = cumsum(n)) %>%
    knitr::kable()
```

### Additional Suspicious Flags

```{r}
flags$flag_values %>%
    filter(group == "suspicious") %>%
    group_by(Vrid) %>%
    summarise(flags = sum(value)) %>%
    count(flags) %>%
    arrange(desc(flags)) %>%
    mutate(cumulative_n = cumsum(n)) %>%
    knitr::kable()
```

### All Flags

Respondents with 4 or more flags are intended to be excluded.

```{r}
flags$flag_values %>%
    group_by(Vrid) %>%
    summarise(flags = sum(value)) %>%
    count(flags) %>%
    arrange(desc(flags)) %>%
    mutate(cumulative_n = cumsum(n)) %>%
    knitr::kable()
```

## Exclusion Summary

Respondents are flagged as invalid and exluded if crossing a threshold of acceptable flags:

```{r}
# all unique respondents to the survey
svy_all$person %>%
    distinct(id) %>% 
    nrow()

# valid respondents used for analysis
valid <- svy$person %>%
    left_join(flags$flag_totals, by = "Vrid") %>%
    filter(flag < 4 | is.na(flag)) 
valid %>%
    distinct(id) %>%
    nrow()

# note that not all of the valid respondents are marked as complete
count(valid, Vstatus)
```
