---
title: "Find Disagreements in Implan (536) Sectoring Schemes"
date: '`r strftime(Sys.time(), format = "%B %d, %Y")`'
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '')
```

```{r, message = FALSE}
library(readxl)
library(dplyr)
library(implan)
library(tidyr)
```

## Motivation

Running Implan depends on mapping spending categories ("Food - Groceries", etc.) to implan sectors. We currently store these sectoring schemes (or category-sector crosswalks) separately by activity (fish, hunt, etc.). For efficiency, we should consider using a master sector scheme as a single source of truth, and only change it when (1) new categories are needed, or (2) the sectoring scheme needs updating. 

However, there is disagreement between the 4 sectoring schemes examined. As far as I can tell, these shouldn't disagree. If that is the case, then we should fix these discrepancies in a new master sectoring scheme.

An output (Excel) master table [is downloadable here](https://github.com/southwick-associates/B4W-19-01/blob/master/data/interim/compare-sectoring.xlsx) (and R code for this analysis [is stored here](https://github.com/southwick-associates/B4W-19-01/blob/master/code/summary/compare-implan-sectoring.Rmd)).

### Sectoring Scheme

For reference, a few rows of the hunting sectoring scheme (note the leading 3000 was stripped from commodity sector IDs for comparison purposes):

```{r}
# load data
acts <- c("oia", "hunt", "fish", "wildlife")
infile <- "../../data/raw/implan/category_to_sector536.xlsx"
outfile <- "../../data/interim/compare-sectoring.xlsx"

ls <- acts %>%
    sapply(function(x) read_excel(infile, sheet = x) %>% mutate(act = x), simplify = FALSE)

# strip the 3000 sector designator to also test for differences in Ind/Comm
ls <- lapply(ls, function(x) {
    mutate(x, sector = ifelse(sector > 1000, sector - 3000, sector))
})

# make sure I understand the dimension
# - all TRUE (i.e., it's unique by category-sector)
# sapply(ls, function(x) {
#     nrow(distinct(x, category, sector)) == nrow(x)
# })

head(ls[[2]], 3) %>% knitr::kable()
```

## Show Duplication

There are 3 relevant variables that can potentionally disagree between activity sectoring schemes:

- Share: The proportion of the category spending allocated to a sector
- Retail: "Yes" or "No"
- Group: "Ind" (industry) or "Comm" (commodity)

### Share Disagreement

```{r}
# get category-sectors with some disagreement on var & show for each activity
# - note that NA can generally be ignored
show_disagree <- function(var, joinvars = c("category", "sector")) {
    var <- enquo(var)
    all_test <- bind_rows(ls) %>%
        distinct(category, sector, !! var)
    dup <- count(all_test, category, sector) %>% filter(n > 1)
    all_spread <- bind_rows(ls) %>%
        select(category, sector, act, !! var) %>%
        spread(act, !! var)
    semi_join(all_spread, dup, by = joinvars) %>%
        arrange(category, sector) %>%
        mutate()
}
disagree_share <- show_disagree(share, "category")
disagree_share %>% knitr::kable()
```

### Retail Disagreement

```{r}
disagree_retail <- show_disagree(retail) %>% mutate(disagree_retail = 1)
knitr::kable(disagree_retail)
```

### Industry/Commodity Disagreement

```{r}
disagree_group <- show_disagree(group)
knitr::kable(disagree_group)
```

### Master

Preparing a master table with one row per category-sector. Flag variables are included for disagreement, and corresponding variables are set to missing. The idea is that this table can be easily manually edited to fix discrepancies.

```{r}
master <- bind_rows(ls) %>%
    group_by(category, sector) %>%
    slice(1L) %>%
    ungroup() %>%
    select(-act)

update_master <- function(master, df, joinvars = c("category", "sector")) {
    flag_value <- deparse(substitute(df))
    varname <- sub(".*_", "", flag_value)
    x <- semi_join(master, df, by = joinvars)
    x[[flag_value]] <- "Y"
    x[[varname]] <- NA
    bind_rows(x, anti_join(master, df, by = joinvars))
}
master <- update_master(master, disagree_share, "category")
master <- update_master(master, disagree_retail)
master <- update_master(master, disagree_group)

master <- master %>%
    arrange(desc(disagree_share), desc(disagree_retail), desc(disagree_group))

master_disagree <- master %>%
    filter(is.na(share) | is.na(retail) | is.na(group))
knitr::kable(master_disagree)
```

```{r}
# save relevant tables as Excel to share with Tom/Lisa
# xlsx_initialize_workbook(f)
xlsx_write_table(master, outfile)
xlsx_write_table(master_disagree, outfile)
```

